### 2015-11-19 Draft_Paper.tex
Draft Paper
Initial Commit

% TEMPLATE for Usenix papers, specifically to meet requirements of
%  USENIX '05
% originally a template for producing IEEE-format articles using LaTeX.
%   written by Matthew Ward, CS Department, Worcester Polytechnic Institute.
% adapted by David Beazley for his excellent SWIG paper in Proceedings,
%   Tcl 96
% turned into a smartass generic template by De Clarke, with thanks to
%   both the above pioneers
% use at your own risk.  Complaints to /dev/null.
% make it two column with no page numbering, default is 10 point

% Munged by Fred Douglis <douglis@research.att.com> 10/97 to separate
% the .sty file from the LaTeX source template, so that people can
% more easily include the .sty file into an existing document.  Also
% changed to more closely follow the style guidelines as represented
% by the Word sample file.

% Note that since 2010, USENIX does not require endnotes. If you want
% foot of page notes, don't include the endnotes package in the 
% usepackage command, below.

% This version uses the latex2e styles, not the very ancient 2.09 stuff.
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\begin{document}

%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Webcam Fuzz Testing: Testing IoT Deployments}

%for single author (just remove % characters)
\author{
{\rm Matthew Elbert}\\
University of Utah
\and
{\rm Jeffrey Kitchen}\\
University of Utah
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

\maketitle

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
\thispagestyle{empty}

\subsection*{Abstract}
Your Abstract Text Goes Here.  Just a few facts.
Whet our appetites.

\section{Introduction}
\subsection{Motivation}

Fuzz testing is a method of testing in which random, potentially invalid inputs are sent to a program or service in order to test for vulnerabilities. It is often used as either a gray or black-box testing platform for security testing. Fuzz testing can be a very cheap and effective implementation of testing as many inputs can be generated, sent, and analyzed automatically, without the need for a human to monitor. Because the world has become more internet-connected than ever, fuzz testing can be an important tool for developers as network-facing interfaces can experience any input, and need to be tested for this randomness. However, many functions are very state-driven, and a true, random test may only test a single interface, and not the whole system. Because of this, many of these fuzz testers must be stateful in order to do a complete test. But because a truly random input would take infinite time to find all possible inputs, a mutation of correct inputs approach is often implemented.

\subsection{Problem}

For this project, we were tasked with designing, implementing and evaluating an automated tester for a networking service. This is meant to evaluate the value of fuzz testing on a network, with the goal of hopefully finding a previously undiscovered bug. A very basic and highly proliferated technology deployed on the internet is an HTTP server. But because of this prevalence, popular servers such as Apache have been thoroughly tested and documented. However, more and more devices are being connected, with an uptake in the Internet of Things (IoT) mentality. Therefore, we chose wireless IP cameras as the platform to fuzz test. These are some of the most widely available IoT devices for consumers. We found that the two devices we purchased ran basic HTTP servers, and we could use tools made for these applications.

\section{Related Work}

We looked at papers like SecFuzz~\cite{secfuzz} and SNOOZE~\cite{snooze} as well as tools like AutoFuzz~\cite{autofuzz}

\section{Proposed Solution}

Use solutions for HTTP fuzzing, e.g. Pathoc, to fuzz the HTTP servers running on webcams.

\section{Implementation}

We used Pathoc for crafted malice towards the mini\_httpd and DLink servers.

\section{Results}

{\footnotesize \bibliographystyle{acm}
\bibliography{biblio}}

\theendnotes

\end{document}

### 2015-11-22 Draft Paper/Draft_Paper.tex
more stuff
draft_round2

--- 2015-11-19 Draft_Paper.tex
@@
 \documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{usenix,epsfig,endnotes}
+\usepackage{usenix,epsfig,url}
 \begin{document}
@@
 \subsection*{Abstract}
-Your Abstract Text Goes Here.  Just a few facts.
-Whet our appetites.
+Fuzz testing, or fuzzing, is a simple method to find bugs and vulnerabilities in programs. We use fuzzing methods to attempt to identify security vulnerabilities in two Wi-Fi cameras.
 
@@
 
-For this project, we were tasked with designing, implementing and evaluating an automated tester for a networking service.
+For this project, we explored the possibility of implementing and evaluating an automated tester for a networking service.
 This is meant to evaluate the value of fuzz testing on a network, with the goal of hopefully finding a previously undiscovered bug.
@@
 
+One reason we thought it would be interesting as well as important to test these IP cameras is because they are widely used in security systems today.
+It would likely be a bad thing if an outsider could shut down or otherwise impair the function of your security cameras.
+One main goal we had during this experiment was to identify security vulnerabilities in the cameras through fuzzing, to find out if a potential attacker could impair the camera's function.
+
 \section{Related Work}
+??CAN we find a paper or related work where other IoT devices were similarly tested for security vulnerabilities??
 
@@
 
-\section{Proposed Solution}
+\section{Experiment Setup}
+In this section we describe details about the setup of our experiment, the
+cameras we used, how we gathered information and discovered interesting ways to fuzz test them, and the tools and programs that aided us.
 
-Use solutions for HTTP fuzzing, e.g. Pathoc, to fuzz the HTTP servers running on webcams.
+\subsection{IP Cameras}
+The two cameras we purchased were a D-Link Day \& Night Wi-Fi Camera (DCS-934L)~\cite{dlinkCam} and a ???..............????
+.
+Though both cameras supported many network protocols, we focused on fuzzing the \textit{alphapd} and \textit{mini-httpd} HTTP servers and the application layers of each of the cameras.
+
+\subsubsection{Information Gathering}
+When we first purchased the cameras, we set them up for normal operation and began playing with the provided tools to learn about how they worked.
+Each of the cameras, after being set up properly, were assigned IP addresses where their main web pages could be accessed.
+Access to these web pages is protected by username/password combinations defined during the setup process.
+Once logged in, a number of functions and features are available.
+For example, on the D-Link camera, the user can manually select day or night mode, enable or disable motion or sound detection, turn on and off notification emails, etc.
+
+The first step in identifying network protocols that would be interesting and `fuzzable' was to capture some traffic from the cameras in Wireshark~\cite{wireshark}.
+We also looked at the HTML source behind the web pages to discover potential attack points.
+We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions.
+
+Though the cameras boasted support for many network protocols, most of the functionality was very limited and only supported client protocols.
+Both cameras did have small HTTP servers, though, which are much more interesting to fuzz.
+We discovered early on that authentication tokens could be easily exposed, making deeper application level access possible.
+We chose to enter the realm of penetration testing a bit because we thought the application layer would potentially reveal more interesting security flaws.
+These were some primary reasons we chose to focus on fuzzing the HTTP servers and application layers.
+
+\subsubsection{Tools}
+We began by exploring a number of available network fuzzers, including AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathoc~\cite{pathod}.
+AFL was complex and we were unable to get it running.
+AutoFuzz had built in support for MSN, SMTP, and FTP protocols.
+Because neither of the cameras had servers for these protocols we chose not to use AutoFuzz.
+Pathoc turned out to be fairly simple and straightforward to use, and so we chose to focus on this tool to drive our testing.
+
+Because pathoc is a Linux, command line driven program, we began coding up a Bash script to structure inputs to pathoc, and collect and analyze outputs.
 
@@
 
+This is where we could describe in more detail specifics about the types of fuzzing we accomplished, the control loop structures of the scripts, categories of data we recorded, pages or applications that we targeted, etc.
+
 \section{Results}
+
+Perhaps the first major discovery we made when in the information-gathering stage of the project was that each of the cameras used HTTP Basic or Digest access authentication, which encodes the username:password combinations.
+Wireshark was able to capture the authentication for logging into the cameras in plain text.
+This has important ramifications, because all an attacker would need to do would be to use Wireshark or some other network protocol analyzer to capture traffic on the network the camera is on.
+Once the authentication token is discovered, an attacker could append it to the header of any HTTP message desired, and the camera would accept it as authentic.
 
@@
 
-\theendnotes
-
 \end{document}

### 2015-11-22 Draft Paper/Draft_Paper.tex
Added to draft - Jeff

--- 2015-11-19 Draft_Paper.tex
@@
 \documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{usenix,epsfig,endnotes}
+\usepackage{usenix,epsfig}
 \begin{document}
@@
 Fuzz testing can be a very cheap and effective implementation of testing as many inputs can be generated, sent, and analyzed automatically, without the need for a human to monitor.
+However, a truely random test input could easily not provide anything useful in a reasonable amount of time.
+Therefore, many solutions (citations needed) propose a different method where random mutation of good inputs is used so that requests that are close to being correct are used.
 Because the world has become more internet-connected than ever, fuzz testing can be an important tool for developers as network-facing interfaces can experience any input, and need to be tested for this randomness.
@@
 Because of this, many of these fuzz testers must be stateful in order to do a complete test.
-But because a truly random input would take infinite time to find all possible inputs, a mutation of correct inputs approach is often implemented.
+Because of many security issues with the current Internet architecture, there are obviosuly some security measures put in place to almost anything that is deployed on a network, even if it is meant to only be local.
+Therefore, something as simples as loggin into an interface needs to be taken into account in order to et more meaningful tests.
 
@@
 
-For this project, we were tasked with designing, implementing and evaluating an automated tester for a networking service.
+In this project, we designed, implemented and evaluated an automated tester for a networking service.
 This is meant to evaluate the value of fuzz testing on a network, with the goal of hopefully finding a previously undiscovered bug.
@@
 We used Pathoc for crafted malice towards the mini\_httpd and DLink servers.
+Pathoc has a built in function to do many requests at one time, but we found that this method had all of the GET requests on a single TCP connection, and therefore made it more difficult to diagnose in programs such as Wireshark.
+Therefore, since Pathoc can easily be implemented using the command line interface, a shell script was used as a wrapper that would invoke Pathoc multiple times, giving a new HTTP request everytime.
+In this way, we could also control fairly easily the commands for Pathoc to run, instead of having a single command run multiple times.
 

### 2015-11-22 Draft Paper/Draft_Paper.tex
Fixing merge problems

--- 2015-11-22 Draft Paper/Draft_Paper.tex
@@
 
-For this project, we explored the possibility of implementing and evaluating an automated tester for a networking service.
+In this project, we designed, implemented and evaluated an automated tester for a networking service.
 This is meant to evaluate the value of fuzz testing on a network, with the goal of hopefully finding a previously undiscovered bug.

### 2015-12-03 Scripts/Jeff/fuzz.sh
tweak script

@@ -77,14 +77,17 @@ else #start fuzzing DLINK camera
 
 for (( i=1; i<=$max; i++))
 do
-  r=$(( $RANDOM % 2 )) #Random [0-1]
+  r=$(( $RANDOM % 100)) #Random [0-99]
   d=$(( ($i*100)/$max ))
   echo -ne "Percent Done: $d \r"
-  modCase=$(( ($i % 7) )) 
+ modCase=$(( ($i % 7) )) 
+#modCase=3 #force only one case for now
  case $modCase in
 0)
-  #valid request
-  pathoc -n 1 -t 5 -e -q -p $ip 'get:/image/jpeg.cgi:b@100,ascii:h"Authorization"="Basic YWRtaW46YjNZb25kQ2FtZmluaXR5TUtF" '  | tee -a "log_$NOW".txt | tee last_cmd.txt | grep 'HTTP/1.[0-1] 2' &> /dev/null
+  #valid request with random 50 chars
+ pathoc -n 1 -t 5 -e -q -p $ip 'get:/image/jpeg.cgi:b@100,ascii:ir,@50h"Authorization"="Basic YWRtaW46YjNZb25kQ2FtZmluaXR5TUtF" '  | tee -a "log_$NOW".txt | tee last_cmd.txt | grep 'HTTP/1.[0-1] 2' &> /dev/null
+  
+  #pathoc -n 1 -t 5 -e -q -p $ip 'get:/:b@100,ascii:ir,@5h"Authorization"="Basic YWR" '  | tee -a "log_$NOW".txt | tee last_cmd.txt | grep 'HTTP/1.[0-1] 2' &> /dev/null
   ;;
 1)
   #long get request
@@ -109,7 +112,7 @@ do
  ;;  
 *)
   #post
-  pathoc -n 1 -t 5 -e -p -q  $ip 'post:/nightmodecontrol.cgi:b"IRLed='$r'":h"Authorization"="Basic YWRtaW46YjNZb25kQ2FtZmluaXR5TUtF" ' | tee -a "log_$NOW".txt | tee last_cmd.txt | grep 'HTTP/1.[0-1] 2' &> /dev/null
[…]

### 2015-12-03 Draft Paper/Draft_Paper.tex
paper update
paper update

@@
 Fuzz testing can be a very cheap and effective implementation of testing as many inputs can be generated, sent, and analyzed automatically, without the need for a human to monitor.
-However, a truely random test input could easily not provide anything useful in a reasonable amount of time.
+However, a truly random test input could easily not provide anything useful in a reasonable amount of time.
 Therefore, many solutions (citations needed) propose a different method where random mutation of good inputs is used so that requests that are close to being correct are used.
@@
 Because of this, many of these fuzz testers must be stateful in order to do a complete test.
-Because of many security issues with the current Internet architecture, there are obviosuly some security measures put in place to almost anything that is deployed on a network, even if it is meant to only be local.
-Therefore, something as simples as loggin into an interface needs to be taken into account in order to et more meaningful tests.
+Because of many security issues with the current Internet architecture, there are obviously some security measures put in place to almost anything that is deployed on a network, even if it is meant to only be local.
+Therefore, something as simple as logging into an interface needs to be taken into account in order to get more meaningful tests.
 
@@
 \subsection{IP Cameras}
-The two cameras we purchased were a D-Link Day \& Night Wi-Fi Camera (DCS-934L)~\cite{dlinkCam} and a ???..............????
-.
+The two cameras we purchased were a D-Link Day \& Night Wi-Fi Camera (DCS-934L)~\cite{dlinkCam} and a Pyle Home Indoor Wireless/Wired P2P IP Network Camera (PIPCAM5).
 Though both cameras supported many network protocols, we focused on fuzzing the \textit{alphapd} and \textit{mini-httpd} HTTP servers and the application layers of each of the cameras.
@@
 
+We found the following cgi pages with valid HTTP POST commands for the DLINK camera:
+
+\begin{enumerate}
+	\item /audiocontrol.cgi - METHOD=``POST" name=``AudioMute" value=``[0$\mid$1]"
+	\item /nightmodecontrol.cgi - METHOD=``POST" name=``IRLed" value=``[0$\mid$1]"
+	\item /image/jpeg.cgi
+\end{enumerate}
+
+We found the following cgi pages for the Pyle camera:
+\begin{enumerate}
+	\item /decoder\_control.cgi?command=[0$\mid$100]
+	\newline Valid command numbers:
+	\begin{verbatim}
+	var R320_240=8;
+	var R640_480=32;
+	var ptz_type=0;	
+	if(top.client_minor==4) ptz_type=1;
+	var PTZ_STOP=1;
+	var TILT_UP=0;
+	var TILT_UP_STOP=1;
+	var TILT_DOWN=2;
+	var TILT_DOWN_STOP=3;
+	var PAN_LEFT=4;
+	var PAN_LEFT_STOP=5;
+	var PAN_RIGHT=6;
+	var PAN_RIGHT_STOP=7;
+	var PTZ_LEFT_UP=90;
+	var PTZ_RIGHT_UP=91;
+	var PTZ_LEFT_DOWN=92;
+	var PTZ_RIGHT_DOWN=93;
+	var PTZ_CENTER=25;
+	var PTZ_VPATROL=26;
+	var PTZ_VPATROL_STOP=27;
+	var PTZ_HPATROL=28;
+	var PTZ_HPATROL_STOP=29;
+	var PTZ_PELCO_D_HPATROL=20;
+	var PTZ_PELCO_D_HPATROL_STOP=21;
+	var IO_ON=94;
+	var IO_OFF=95;
+	\end{verbatim}
+	\item camera\_control.cgi?param='+param+'\&value='+value; 
+\end{enumerate}
+
 \subsubsection{Tools}
@@
 
-This is where we could describe in more detail specifics about the types of fuzzing we accomplished, the control loop structures of the scripts, categories of data we recorded, pages or applications that we targeted, etc.
+We wrote a bash script that would take the IP address, camera ID (1=PYLE, 2=DLINK), and number of fuzzing tests as arguments.
+Each camera had its own set of fuzzing commands, to make more use of the details we gathered from each individual cameras web page.
+
+We also wrote a script to scour the log files and aggregate the total number of responses in various categories.
+We used some of this data for the Pyle camera to generate figures~\ref{fig:Pyle_Good_CGI} and ~\ref{fig:Pyle_Rand_CGI}.
+
+[EDIT ME]This is where we could describe in more detail specifics about the types of fuzzing we accomplished, the control loop structures of the scripts, categories of data we recorded, pages or applications that we targeted, etc.
 
@@
 
+[EDIT ME]
+As of today [Nov 28,2015] we have run about 18,000 fuzzing tests.
+We are in the process of aggregating data and trying to understand how best to display it.
+We have not as of yet found any input that would disable the cameras completely, though some inputs do cause slow downs.
+Figure~\ref{fig:Pyle_Good_CGI} sums up the distribution of three separate test run sizes for CGI commands with good numeric inputs (within range 1-100).
+Figure~\ref{fig:Pyle_Rand_CGI} shows the same number of tests for purely random alpha-numeric commands.
+\begin{figure*}
+\centering
+\includegraphics[width=0.9\linewidth]{Pyle_Good_CGI}
+\caption{ 5550 fuzz tests on Pyle camera with valid commands}
+\label{fig:Pyle_Good_CGI}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.9\linewidth]{Pyle_Rand_CGI}
+\caption{5550 fuzz tests on Pyle camera with random commands}
+\label{fig:Pyle_Rand_CGI}
+\end{figure*}
+
 {\footnotesize \bibliographystyle{acm}

### 2015-12-03 Draft Paper/Draft_Paper.tex
paper update and pwrpoint

@@
 
-\subsubsection{Tools}
+\subsection{Tools}
 We began by exploring a number of available network fuzzers, including AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathoc~\cite{pathod}.
@@
 Because pathoc is a Linux, command line driven program, we began coding up a Bash script to structure inputs to pathoc, and collect and analyze outputs.
+
+[TODO]write more about pathoc, how we drove pathoc. We can also include raspberry pi work.
 
@@
 [EDIT ME]This is where we could describe in more detail specifics about the types of fuzzing we accomplished, the control loop structures of the scripts, categories of data we recorded, pages or applications that we targeted, etc.
+This would be a good place to mention the different categories of fuzzing: pure random, why we chose get/post at different application levels.
 
@@
 Figure~\ref{fig:Pyle_Rand_CGI} shows the same number of tests for purely random alpha-numeric commands.
+
+This would be a good place to mention average times for each type of fuzzing tests.
+
+Draw some conclusions from the data. Find bugs? Or the conclusion could be that we found interesting errors, or perhaps we didn't find any bugs.
+
+\section{Conclusion}
+We began with the hypothesis... we presented ... our results showed...
+
+Mention the idea for recording the video to measure lag and potential for DoS attacks.
+
 \begin{figure*}

### 2015-12-04 Draft Paper/Draft_Paper.tex
minor update paper & script
Paper: Reworded 3.1.1, added tables, removed figures
Script: grep 20* did not work, replaced w/ grep HTTP/1.1 200

--- 2015-12-03 Draft Paper/Draft_Paper.tex
@@
 \subsection*{Abstract}
-Fuzz testing, or fuzzing, is a simple method to find bugs and vulnerabilities in programs. We use fuzzing methods to attempt to identify security vulnerabilities in two Wi-Fi cameras.
+Fuzz testing, or fuzzing, is a simple, automated method to find bugs and vulnerabilities in programs.
+We use fuzzing methods on two different types of Wi-Fi cameras in order to evaluate the efficacy of fuzz testing on these recent types of IoT deployments.
 
@@
 For example, on the D-Link camera, the user can manually select day or night mode, enable or disable motion or sound detection, turn on and off notification emails, etc.
+The Pyle camera also allowed Panning and Tilting via the network.
+
+Though the cameras boasted support for many network protocols, most of the functionality was very limited and only supported client protocols.
+Both cameras did have small HTTP servers, though, which are much more interesting to fuzz, as they will more readily accept the inputs that we would give them.
 
@@
 We also looked at the HTML source behind the web pages to discover potential attack points.
-We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions.
+We discovered early on that authentication tokens could be easily exposed, making deeper application level access possible.
+This was possible because the cameras only used Basic Authentication, where the encoded user name and password are store in plaintext in the requests.
+From here, we could automate the fuzzer to get past the HTTP ``front door" and send sensitive commands that require authentication.
+This way, we could also test the application layer being run on these camera, rather than the HTTP protocol layer.
+We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions., and these pages were used to fuzz application layers.
 
-Though the cameras boasted support for many network protocols, most of the functionality was very limited and only supported client protocols.
-Both cameras did have small HTTP servers, though, which are much more interesting to fuzz.
-We discovered early on that authentication tokens could be easily exposed, making deeper application level access possible.
-We chose to enter the realm of penetration testing a bit because we thought the application layer would potentially reveal more interesting security flaws.
-These were some primary reasons we chose to focus on fuzzing the HTTP servers and application layers.
-
-We found the following cgi pages with valid HTTP POST commands for the DLINK camera:
+We found the following cgi pages for the DLINK camera:
 
@@
 
+It is important to note that the DLink camera implemented the CGI commands using a HTTP POST method, using the parameters that were passed to it from the application with a command in the body.
+The Pyle camera, however, took the parameters from the application and then formatted a HTTP GET command, with the CGI commands in the HTTP path, and no body.
+
 \subsubsection{Tools}
@@
 We have not as of yet found any input that would disable the cameras completely, though some inputs do cause slow downs.
-Figure~\ref{fig:Pyle_Good_CGI} sums up the distribution of three separate test run sizes for CGI commands with good numeric inputs (within range 1-100).
-Figure~\ref{fig:Pyle_Rand_CGI} shows the same number of tests for purely random alpha-numeric commands.
-\begin{figure*}
+Table~\ref{tab:Pyle_Good_CGI} sums up the distribution of three separate test run sizes for CGI commands with good numeric inputs (within range 1-100).
+Table~\ref{tab:Pyle_Rand_CGI} shows the same number of tests for purely random alpha-numeric commands.
+
+\begin{table}
 \centering
-\includegraphics[width=0.9\linewidth]{Pyle_Good_CGI}
-\caption{ 5550 fuzz tests on Pyle camera with valid commands}
-\label{fig:Pyle_Good_CGI}
-\end{figure*}
+	\begin{tabular}{ |c|c|c|c|c| }
+		\hline
+		\# Tests & 50 & 500 & 5000 & 50000 \\
+		\hline
+		\hline
+		Time(s) & 87 & 865 & 3721 & 98260\\
+		Timeouts & 1 & 5 & 187 & 3954 \\
+		HTTP 3XX & 0 & 0 & 0 & 0\\
+		HTTP 4XX & 13 & 106 & 1236 & 12284\\
+		HTTP 5XX & 1 & 5 & 69 & 628\\
+		\hline
+	\end{tabular}
+	\caption{55550 fuzz tests on Pyle camera with CGI commands within accepted range}
+	\label{tab:Pyle_Good_CGI} 
+\end{table}
 
-\begin{figure*}
+\begin{table}
 \centering
-\includegraphics[width=0.9\linewidth]{Pyle_Rand_CGI}
-\caption{5550 fuzz tests on Pyle camera with random commands}
-\label{fig:Pyle_Rand_CGI}
-\end{figure*}
+	\begin{tabular}{ |c|c|c|c| }
+		\hline
+		\# Tests & 50 & 500 & 5000 \\
+		\hline
+		\hline
+		Time(s) & 89 & 704 & 7545 \\
+		Timeouts & 0 & 0 & 31  \\
+		HTTP 3XX & 0 & 0 & 0 \\
+		HTTP 4XX & 2 & 8 & 91 \\
+		HTTP 5XX & 0 & 0 & 1 \\
+		\hline
+	\end{tabular}
+	\caption{5550 fuzz tests on Pyle camera with random length, random content CGI}
+	\label{tab:Pyle_Rand_CGI} 
+\end{table}
+
+%\begin{figure*}
+%\centering
+%\includegraphics[width=0.9\linewidth]{Pyle_Good_CGI}
+%\caption{ 5550 fuzz tests on Pyle camera with valid commands}
+%\label{fig:Pyle_Good_CGI}
+%\end{figure*}
+
+%\begin{figure*}
+%\centering
+%\includegraphics[width=0.9\linewidth]{Pyle_Rand_CGI}
+%\caption{5550 fuzz tests on Pyle camera with random commands}
+%\label{fig:Pyle_Rand_CGI}
+%\end{figure*}
 

### 2015-12-04 Scripts/Jeff/fuzz.sh

@@ -45,7 +45,7 @@ do
 	d=$(( ($i*100)/$max ))
 	r=$(( $RANDOM % 100 + 1 )) #Random [1..100]
 	
-pathoc -n 1 -t 5 -e -p -q $ip "$cmd$r$b1$auth" | tee -a "log_$NOW".txt | tee last_cmd.txt | grep 'HTTP/1.1 2*' &> /dev/null
+pathoc -n 1 -t 5 -e -p -q $ip "$cmd$r$b1$auth" | tee -a "log_$NOW".txt | tee last_cmd.txt | grep 'HTTP/1.1 200' &> /dev/null
 
 	if [ $? == 0 ]; then
 		good=$(( $good+1 ))

### 2015-12-04 Draft Paper/Draft_Paper.tex
Updated References
Wrote a whole lot for Section 2 Related Work. Added more citations in
the biblio as well.

@@
 \section{Related Work}
+One of the first attempts at a random input tester was done by Miller et.
+al.~\cite{millerUNIX}.
+Their work consisted of creating small programs for UNIX that would generate ransom strings that would then be piped to various programs of a few UNIX distributions.
+They found, at the time of publication in 1990, that they could cause roughly a third of the tested utilities to crash or hang with the generated inputs, some of which even cause UNIX crashes.
+
+SNOOZE~\cite{snooze} is a network fuzzing protocol that is used to test the security of network protocols.
+In their approach, they show how the true random testing of fuzzing would not be desirable for the protocols in which they wanted to test.
+Therefore, they created a method in which the state machines of protocols are defined, and then transversed through the testing.
+SNOOZE chose to focus on the Session Initiation Protocol (SIP), which is a key protocol for VoIP calls.
+
+SecFuzz~\cite{secfuzz} was another implementation of testing security protocols.
+For their tests, they focused on the Internet Key Exchange (IKE) protocols, and gave their fuzzer the necessary cryptographic functions.
+Their method entailed sending correct inputs in order to get the state-driven protocol into a desired state, and then slowly mutate good inputs for that state until something undesirable happened.
+They relied on what they called ``fuzz operators" that would set certain fields, payloads or messages to certain values (eg.
+random or zero) to try and coax an undesirable response.
+
+AspFuzz~\cite{aspfuzz} was another type of fuzzer, but this one was created and tested in protocols such as POP and HTTP.
+Their implementation had a user supply the protocol specification.
+It would then generate attacks that would either be long strings, known incorrect characters, known out of bounds numbers, format strings, changing the number of fields, and removing delimiters.
+
+While these papers looked like they had gathered results from their fuzz testing, they did not release their prototype to the public, and therefore we had to find other publicly available tools that would be able to create fuzz tests.
+A few of the papers read, such as AspFuzz, mentioned the Peach Fuzzing Platform~\cite{peach} as a tool widely used in this type of testing.
+We were also able to find widely available tools like AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathod/Pathoc~\cite{pathoc}.
+More discussion on these tools is presented in section 3.1.2.
+
 ??CAN we find a paper or related work where other IoT devices were similarly tested for security vulnerabilities??
-
-We looked at papers like SecFuzz~\cite{secfuzz} and SNOOZE~\cite{snooze} as well as tools like AutoFuzz~\cite{autofuzz}
 
@@
 We also wrote a script to scour the log files and aggregate the total number of responses in various categories.
-We used some of this data for the Pyle camera to generate figures~\ref{fig:Pyle_Good_CGI} and ~\ref{fig:Pyle_Rand_CGI}.
+We used some of this data for the Pyle camera to generate tables~\ref{tab:Pyle_Good_CGI} and ~\ref{tab:Pyle_Rand_CGI}.
 

### 2015-12-05 Draft Paper/Draft_Paper.tex
Paper Update
Added a bunch of stuff. 3.1.2 Tools is rewritten, Section 4 is split
into two subsections, some more results given, etc.

@@
 \subsubsection{Tools}
-We began by exploring a number of available network fuzzers, including AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathoc~\cite{pathod}.
-AFL was complex and we were unable to get it running.
-AutoFuzz had built in support for MSN, SMTP, and FTP protocols.
-Because neither of the cameras had servers for these protocols we chose not to use AutoFuzz.
-Pathoc turned out to be fairly simple and straightforward to use, and so we chose to focus on this tool to drive our testing.
+We began by exploring a number of available network fuzzers, including Peach, AutoFuzz, American Fuzzy Lop (AFL), and Pathoc.
+In investigating AFL, we found that it was a tool mainly for file testing, where good files as inputs to tools would be mutated and input back into a program for evaluation.
+We could have used this to create a file with a valid GET request, ran AFL to mutate, and send the file through something like netcat, but this would be more difficult to control in what get sent to the servers.
 
-Because pathoc is a Linux, command line driven program, we began coding up a Bash script to structure inputs to pathoc, and collect and analyze outputs.
+AutoFuzz had built in support for MSN, SMTP, and FTP protocols, and relied on capturing actual traffic in order to create a state machine.
+While we did find that both of the cameras used in testing supported both SMTP and FTP, they were only clients, and therefore less likely to accept inputs.
+We were not able to find HTTP support for AutoFuzz, so this method was abandoned.
+
+Peach was another platform that was looked at extensively.
+The peach platform relies on ``pits" that define the fields in the standard being tested, as well as the procedure that should be used in testing.
+Their website shows that they have support for protocols such as HTTP, DHCP, IPv4, IPv6, and IoT protocols like CoAP.
+However, these pits are how this company makes money, and we were not willing to purchase them in order to evaluate if they would work for us or not.
+
+Pathoc turned out to be fairly simple and straightforward to use, as it was just a command line interface tool that generated HTTP requests such as GET and POST.
+Because we focused on HTTP, this single protocol application was still very appealing to us.
+This program allowed us to specify the type of HTTP command, and inject whatever we wanted into the header and body fields while still creating a command with valid syntax.
+It also has fuzzing capabilities as it is able to inject random bytes anywhere in the request, as well as generate random strings of a desired length and place them in portions of a request.
+Because of its ease of use and the capability to be used in a simple Bash script, we chose Pathoc v0.14 as our fuzzing platform.
 
@@
 
+\subsection{Pathoc Structure}
 We used Pathoc for crafted malice towards the mini\_httpd and DLink servers.
@@
 [EDIT ME]This is where we could describe in more detail specifics about the types of fuzzing we accomplished, the control loop structures of the scripts, categories of data we recorded, pages or applications that we targeted, etc.
+
+\subsection{Platforms}
+The primary vehicle for running Pathoc in a Bash script was using Oracle's VM VirtualBox 5.0.10 running on two separate Windows 10 laptops.
+One computer ran a 32-bit Ubuntu 12.04 VM with 2.0GiB of dedicated RAM.
+The other computer was using the All-in-one SDN App Development Starter VM, an image based off of 64-bit Ubuntu 14.04, from SDNHub.org.
+
+Because these tests can take a significant amount of time, and these computers are also used for other things, a third platform was used to collect fuzzing data.
+A Raspberry Pi 2 model B (RPi) was used so that Pathoc could be run for an extended amount of time (e.g.
+over 24 hours) without the platform needing to be used for something else.
+The Raspberry Pi was running Raspbian, a derivation of Debian, kernel version 4.1.7.
+The Pi used a USB 802.11n WiFi adapter to connect to the local network, and the fuzzing script and repository for the log files were placed in a connected 16GB USB flash drive.
 
@@
 Table~\ref{tab:Pyle_Rand_CGI} shows the same number of tests for purely random alpha-numeric commands.
+
+An interesting result was also the difference in the time taken to run the same command on a Ubuntu VM comapred to the Raspberry Pi.
+We noticed that although the small computer is very powerful, it had a significant time overhead in our setup.
+The results of a test consisting of 5000 valid CGI commands to the Pyle camera is shown in table~\ref{tab:VMvsPi}.
+As we can see, they both generated a similar amount of HTTP responses in the 400 and 500 range, but the Rpi took almost 450\% longer to do it.
+We suspect it may have to do with the smaller computer having slower I/O speeds for both the USB flash drive and the network interface.
+All USB ports are also run on one controller, leading to a slowdown if many are used at the same time.
 
@@
 
+\begin{table}
+\centering
+	\begin{tabular}{ |c|c|c| }
+		\hline
+		~ & Ubuntu 12.04 VM & RPi 2\\
+		\hline
+		\hline
+		Time(s) & 3909 & 17555 \\
+		Timeouts & 193 & 545  \\
+		HTTP 3XX & 0 & 0 \\
+		HTTP 4XX & 1227 & 1210 \\
+		HTTP 5XX & 65 & 62 \\
+		\hline
+	\end{tabular}
+	\caption{5000 Random CGI commands on the Ubuntu VM and RPi platforms}
+	\label{tab:VMvsPi} 
+\end{table}
+
 %\begin{figure*}
@@
 
+\subsection*{Acknowledgments}
+We would like to thank our shepherd, Dr. Eric Eide in providing invaluable insight and assistance with two poor ECE students completing a CS project.
+
 {\footnotesize \bibliographystyle{acm}

### 2015-12-05 Draft Paper/Draft_Paper.tex
small change

--- 2015-12-04 Draft Paper/Draft_Paper.tex
@@
 \subsection*{Abstract}
-Fuzz testing, or fuzzing, is a simple, automated method to find bugs and vulnerabilities in programs.
-We use fuzzing methods on two different types of Wi-Fi cameras in order to evaluate the efficacy of fuzz testing on these recent types of IoT deployments.
+Fuzz testing, or fuzzing, is a simple method to find bugs and vulnerabilities in programs. We use fuzzing methods to attempt to identify security vulnerabilities in two Wi-Fi cameras.
 
@@
 For example, on the D-Link camera, the user can manually select day or night mode, enable or disable motion or sound detection, turn on and off notification emails, etc.
-The Pyle camera also allowed Panning and Tilting via the network.
-
-Though the cameras boasted support for many network protocols, most of the functionality was very limited and only supported client protocols.
-Both cameras did have small HTTP servers, though, which are much more interesting to fuzz, as they will more readily accept the inputs that we would give them.
 
@@
 We also looked at the HTML source behind the web pages to discover potential attack points.
+We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions.
+
+Though the cameras boasted support for many network protocols, most of the functionality was very limited and only supported client protocols.
+Both cameras did have small HTTP servers, though, which are much more interesting to fuzz.
 We discovered early on that authentication tokens could be easily exposed, making deeper application level access possible.
-This was possible because the cameras only used Basic Authentication, where the encoded user name and password are store in plaintext in the requests.
-From here, we could automate the fuzzer to get past the HTTP ``front door" and send sensitive commands that require authentication.
-This way, we could also test the application layer being run on these camera, rather than the HTTP protocol layer.
-We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions., and these pages were used to fuzz application layers.
+We chose to enter the realm of penetration testing a bit because we thought the application layer would potentially reveal more interesting security flaws.
+These were some primary reasons we chose to focus on fuzzing the HTTP servers and application layers.
 
-We found the following cgi pages for the DLINK camera:
+We found the following cgi pages with valid HTTP POST commands for the DLINK camera:
 
@@
 
-It is important to note that the DLink camera implemented the CGI commands using a HTTP POST method, using the parameters that were passed to it from the application with a command in the body.
-The Pyle camera, however, took the parameters from the application and then formatted a HTTP GET command, with the CGI commands in the HTTP path, and no body.
-
-\subsubsection{Tools}
+\subsection{Tools}
 We began by exploring a number of available network fuzzers, including AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathoc~\cite{pathod}.
@@
 We have not as of yet found any input that would disable the cameras completely, though some inputs do cause slow downs.
-Table~\ref{tab:Pyle_Good_CGI} sums up the distribution of three separate test run sizes for CGI commands with good numeric inputs (within range 1-100).
-Table~\ref{tab:Pyle_Rand_CGI} shows the same number of tests for purely random alpha-numeric commands.
+Figure~\ref{fig:Pyle_Good_CGI} sums up the distribution of three separate test run sizes for CGI commands with good numeric inputs (within range 1-100).
+Figure~\ref{fig:Pyle_Rand_CGI} shows the same number of tests for purely random alpha-numeric commands.
 
-\begin{table}
+This would be a good place to mention average times for each type of fuzzing tests.
+
+Draw some conclusions from the data. Find bugs? Or the conclusion could be that we found interesting errors, or perhaps we didn't find any bugs.
+
+\section{Conclusion}
+We began with the hypothesis... we presented ... our results showed...
+
+Mention the idea for future work recording the video to measure lag and potential for DoS attacks. Future work in fuzzing other protocols.
+
+\begin{figure*}
 \centering
-	\begin{tabular}{ |c|c|c|c|c| }
-		\hline
-		\# Tests & 50 & 500 & 5000 & 50000 \\
-		\hline
-		\hline
-		Time(s) & 87 & 865 & 3721 & 98260\\
-		Timeouts & 1 & 5 & 187 & 3954 \\
-		HTTP 3XX & 0 & 0 & 0 & 0\\
-		HTTP 4XX & 13 & 106 & 1236 & 12284\\
-		HTTP 5XX & 1 & 5 & 69 & 628\\
-		\hline
-	\end{tabular}
-	\caption{55550 fuzz tests on Pyle camera with CGI commands within accepted range}
-	\label{tab:Pyle_Good_CGI} 
-\end{table}
+\includegraphics[width=0.9\linewidth]{Pyle_Good_CGI}
+\caption{ 5550 fuzz tests on Pyle camera with valid commands}
+\label{fig:Pyle_Good_CGI}
+\end{figure*}
 
-\begin{table}
+\begin{figure*}
 \centering
-	\begin{tabular}{ |c|c|c|c| }
-		\hline
-		\# Tests & 50 & 500 & 5000 \\
-		\hline
-		\hline
-		Time(s) & 89 & 704 & 7545 \\
-		Timeouts & 0 & 0 & 31  \\
-		HTTP 3XX & 0 & 0 & 0 \\
-		HTTP 4XX & 2 & 8 & 91 \\
-		HTTP 5XX & 0 & 0 & 1 \\
-		\hline
-	\end{tabular}
-	\caption{5550 fuzz tests on Pyle camera with random length, random content CGI}
-	\label{tab:Pyle_Rand_CGI} 
-\end{table}
-
-%\begin{figure*}
-%\centering
-%\includegraphics[width=0.9\linewidth]{Pyle_Good_CGI}
-%\caption{ 5550 fuzz tests on Pyle camera with valid commands}
-%\label{fig:Pyle_Good_CGI}
-%\end{figure*}
-
-%\begin{figure*}
-%\centering
-%\includegraphics[width=0.9\linewidth]{Pyle_Rand_CGI}
-%\caption{5550 fuzz tests on Pyle camera with random commands}
-%\label{fig:Pyle_Rand_CGI}
-%\end{figure*}
+\includegraphics[width=0.9\linewidth]{Pyle_Rand_CGI}
+\caption{5550 fuzz tests on Pyle camera with random commands}
+\label{fig:Pyle_Rand_CGI}
+\end{figure*}
 

### 2015-12-05 Draft Paper/Draft_Paper.tex
Merge remote-tracking branch 'origin/master'
# Conflicts:
#	Draft Paper/Draft_Paper.tex

--- 2015-12-05 Draft Paper/Draft_Paper.tex
@@
 
+[TODO] Revisit this section after the paper has been more fully fleshed out[TODO]
+
+The specific `call for papers' that we target in the presentation of this research is the 9th USENIX Workshop on Offensive Technologies (WOOT '15).
+
 \section{Introduction}
@@
 \subsection{Problem}
+We began this project with some general understanding of fuzzing as a test tool, but without a clear vision of what network services might be interesting or valuable to fuzz.
+After an initial period of exploring current research in fuzzing, we settled on the ultimate goal of our project: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} The project involved several steps: choosing a service to test; deciding how to generate random inputs; determining how to distinguish "good" and "bad" test results; implementing the random tester; and evaluating the effectiveness of the test procedure.
 
-In this project, we designed, implemented and evaluated an automated tester for a networking service.
+In this project, we started with the goal to design, implement and evaluat an automated tester for a networking service.
 This is meant to evaluate the value of fuzz testing on a network, with the goal of hopefully finding a previously undiscovered bug.
@@
 \section{Related Work}
+In the beginning stages of our project, we explored some recent papers related to fuzzing, to give us a more clear idea of how this test technique is currently implemented and how it is evolving.
+Some of the more interesting papers we came across are detailed below.
+
 One of the first attempts at a random input tester was done by Miller et.
 al.~\cite{millerUNIX}.
-Their work consisted of creating small programs for UNIX that would generate ransom strings that would then be piped to various programs of a few UNIX distributions.
-They found, at the time of publication in 1990, that they could cause roughly a third of the tested utilities to crash or hang with the generated inputs, some of which even cause UNIX crashes.
+Their work consisted of creating small programs for UNIX that would generate random strings that would then be piped to various programs of a few UNIX distributions.
+They found, at the time of publication in 1990, that they could cause roughly a third of the tested utilities to crash or hang with the generated inputs, some of which even caused UNIX crashes.
 
@@
 A few of the papers read, such as AspFuzz, mentioned the Peach Fuzzing Platform~\cite{peach} as a tool widely used in this type of testing.
-We were also able to find widely available tools like AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathod/Pathoc~\cite{pathoc}.
+We were also able to find widely available tools like AutoFuzz~\cite{autofuzz}, American Fuzzy Lop (AFL)~\cite{afl}, and Pathod/Pathoc~\cite{pathod}.
 More discussion on these tools is presented in section 3.1.2.
 
-??CAN we find a paper or related work where other IoT devices were similarly tested for security vulnerabilities??
+We tried to find research related to fuzzing internet-connected devices, but were unable to.
+Therefore, we thought this might be a good starting point for our research.
+We thought this would be interesting because more and more `things' are connecting to the internet today, and all of these `Internet of Things' devices have network protocols that would be interesting to test.
 
@@
 Though both cameras supported many network protocols, we focused on fuzzing the \textit{alphapd} and \textit{mini-httpd} HTTP servers and the application layers of each of the cameras.
+We thought the HTTP server protocols and application layers would be the most interesting to fuzz.
+Most of the other protocols supported were only client protocols, which we felt would be less interesting to fuzz, yet still valuable.
+We leave testing these other protocols for future work.
 
@@
 Though the cameras boasted support for many network protocols, most of the functionality was very limited and only supported client protocols.
-Both cameras did have small HTTP servers, though, which are much more interesting to fuzz, as they will more readily accept the inputs that we would give them.
+Both cameras did have small HTTP servers, though, which we felt were much more interesting to fuzz, as they will more readily accept the inputs that we would give them.
 
-The first step in identifying network protocols that would be interesting and `fuzzable' was to capture some traffic from the cameras in Wireshark~\cite{wireshark}.
+The first step we took in identifying network protocols that would be interesting and `fuzzable' was to capture some traffic from the cameras in Wireshark~\cite{wireshark}.
 We also looked at the HTML source behind the web pages to discover potential attack points.
 We discovered early on that authentication tokens could be easily exposed, making deeper application level access possible.
-This was possible because the cameras only used Basic Authentication, where the encoded user name and password are store in plaintext in the requests.
+This was possible because the cameras only used Basic or Digest Authentication, where the encoded user name and password are stored in plain text in the requests.
 From here, we could automate the fuzzer to get past the HTTP ``front door" and send sensitive commands that require authentication.
 This way, we could also test the application layer being run on these camera, rather than the HTTP protocol layer.
-We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions., and these pages were used to fuzz application layers.
+We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions, and we used these pages to fuzz application layers.
 
@@
 In investigating AFL, we found that it was a tool mainly for file testing, where good files as inputs to tools would be mutated and input back into a program for evaluation.
-We could have used this to create a file with a valid GET request, ran AFL to mutate, and send the file through something like netcat, but this would be more difficult to control in what get sent to the servers.
+We could have used this to create a file with a valid GET request, ran AFL to mutate, and send the file through something like netcat, but this would be more difficult to control in what gets sent to the servers.
+This may be a valuable tool for future work in testing the FTP protocols in the cameras.
 
-AutoFuzz had built in support for MSN, SMTP, and FTP protocols, and relied on capturing actual traffic in order to create a state machine.
+AutoFuzz has built in support for MSN, SMTP, and FTP protocols, and relied on capturing actual traffic in order to create a state machine.
 While we did find that both of the cameras used in testing supported both SMTP and FTP, they were only clients, and therefore less likely to accept inputs.
-We were not able to find HTTP support for AutoFuzz, so this method was abandoned.
+We attempted to, but were ultimately not able to capture SMTP or FTP traffic from the cameras.
+AutoFuzz did not have support for HTTP, so this tool was abandoned.
 
 Peach was another platform that was looked at extensively.
-The peach platform relies on ``pits" that define the fields in the standard being tested, as well as the procedure that should be used in testing.
+The Peach platform relies on ``pits" that define the fields in the standard being tested, as well as the procedure that should be used in testing.
 Their website shows that they have support for protocols such as HTTP, DHCP, IPv4, IPv6, and IoT protocols like CoAP.
@@
 
-\subsection{Pathoc Structure}
-We used Pathoc for crafted malice towards the mini\_httpd and DLink servers.
+\subsection{Pathoc}
+We used Pathoc for crafted malice towards the mini\_httpd and alphapd servers.
 Pathoc has a built in function to do many requests at one time, but we found that this method had all of the GET requests on a single TCP connection, and therefore made it more difficult to diagnose in programs such as Wireshark.
@@
 
-We wrote a bash script that would take the IP address, camera ID (1=PYLE, 2=DLINK), and number of fuzzing tests as arguments.
-Each camera had its own set of fuzzing commands, to make more use of the details we gathered from each individual cameras web page.
+\subsection{Scripts}
+We wrote a Bash script that would take the IP address, camera ID (1=PYLE, 2=DLINK), and number of fuzzing tests as arguments.
+Each camera had its own set of fuzzing commands, to make more use of the details we gathered from each individual camera's web page.
 
-We also wrote a script to scour the log files and aggregate the total number of responses in various categories.
+A short example from our script is shown below.
+We used variables to control the inputs to the pathoc command.
+For example \textit{\$cmd} might represent an HTTP GET or POST, \textit{\$b1} represents the contents of the HTTP body, and \textit{\$auth} represents the header with authentication credentials.
+The output is checked, and server responses with \textbf{HTTP/1.1 200} are marked `good' and all others are marked `bad'.
+\begin{verbatim}
+for (( i=1; i<=$max; i++ ))
+do	
+d=$(( ($i*100)/$max ))
+r=$(( $RANDOM % 100 + 1 )) #Random [1..100]
+
+pathoc -n 1 -t 5 -e -p -q $ip "$cmd$r$b1$auth"
+ | tee -a "log_$NOW".txt | tee last_cmd.txt
+ | grep 'HTTP/1.1 200' &> /dev/null
+
+if [ $? == 0 ]; then
+good=$(( $good+1 ))
+#last_out=$(<last_cmd.txt)
+#echo "$last_out" >> "log_$NOW""_good.txt"
+else
+bad=$(( $bad+1 ))
+last_out=$(<last_cmd.txt)
+echo "$last_out" >> "log_$NOW""_bad.txt"
+fi		
+echo -ne "Percent Done: $d  \tGood: $good   
+\tBad: $bad \r"
+done
+\end{verbatim}
+
+It is important to note that if the server doesn't respond with \textbf{HTTP/1.1 200}, it does not necessarily mean that it is bad.
+This is just the metric we used to try and identify possible interesting responses.
+Some interesting responses we found are detailed in the Results section.
+Both cameras were tested with and without authorization credentials, in an effort to identify possible security vulnerabilities.
+
+Fuzzing directed towards the Pyle camera was focused mainly on the \textit{decoder\_control.cgi} page with various commands.
+We tried commands with valid numbers, invalid (large or negative) numbers, and random strings of various length.
+
+Fuzzing directed towards the DLink camera were focused in several different categories, including: valid requests sprinkled with random characters, long (70,000 byte) headers, long (70,000 byte) bodies, long (70,000 byte) HTTP GET requests, and HTTP POST to the \textit{audiocontrol.cgi} and \textit{nightmodecontrol.cgi} pages with valid and invalid command bodies.
+
+We also wrote a separate script to scour the log files and aggregate the total number of responses in various categories.
 We used some of this data for the Pyle camera to generate tables~\ref{tab:Pyle_Good_CGI} and ~\ref{tab:Pyle_Rand_CGI}.
-
-[EDIT ME]This is where we could describe in more detail specifics about the types of fuzzing we accomplished, the control loop structures of the scripts, categories of data we recorded, pages or applications that we targeted, etc.
 
@@
 
+We needed a method of weeding out the `good' responses from the `bad' responses. We decided to look at the several categories of HTTP responses: 
+\begin{enumerate}
+\item HTTP 2xx - successfully received, understood, and accepted.
+\item HTTP 3xx - redirection, or further action required to fulfill request.
+\item HTTP 4xx - client error, or some sort of bad request
+\item HTTP 5xx - server is aware that it has erred or is incapable of fulfilling request.
+\end{enumerate}
+We decided to categorize all but HTTP 2xx responses as `bad'. We also discovered other interesting events:
+\begin{enumerate}
+	\item Response timeouts - pathoc was able to issue the HTTP request but the server didn't respond within the specified time frame.
+	\item Connection timeouts - pathoc could not establish a TCP connection with the server after attempting for some period of time.
+	\item Invalid server response: Server disconnect
+	\item (null) - The server responded but left the identifier blank.
+\end{enumerate}
+
 [EDIT ME]
-As of today [Nov 28,2015] we have run about 18,000 fuzzing tests.
+As of today [Dec 4,2015] we have run more than 250,700 fuzzing tests.
 We are in the process of aggregating data and trying to understand how best to display it.
 We have not as of yet found any input that would disable the cameras completely, though some inputs do cause slow downs.
+Some of the interesting events like connection timeouts may be much more interesting if we could determine that the reason the connection could not be made was that the server had been disabled or was restarting itself.
+There is future work in further analyzing the data that we have collected.
+We have the log files that show the inputs that generated these responses.
+Future work would be to gather and replay these inputs and scrutinize the outputs further.
+
 Table~\ref{tab:Pyle_Good_CGI} sums up the distribution of three separate test run sizes for CGI commands with good numeric inputs (within range 1-100).
@@
 
-\begin{table}
+\begin{table}[here]
 \centering

### 2015-12-05 Draft Paper/Draft_Paper.tex
update paper again dec4 10pm

@@
 The two cameras we purchased were a D-Link Day \& Night Wi-Fi Camera (DCS-934L)~\cite{dlinkCam} and a Pyle Home Indoor Wireless/Wired P2P IP Network Camera (PIPCAM5).
+The cameras support the following protocols:
+\begin{itemize}
+	\itemsep-.5em
+	\item IPv4, ARP, TCP, UDP, ICMP
+	\item DHCP Client
+	\item NTP Client (D-Link only)
+	\item DNS Client
+	\item DDNS Client
+	\item SMTP Client
+	\item FTP Client
+	\item HTTP Server
+	\item PPPoE
+	\item UPnP port forwarding
+	\item RTP, RTSP, RTCP (D-Link only)
+	\item LLTD (D-Link only)
+	\item GPRS (Pyle only)
+\end{itemize}
 Though both cameras supported many network protocols, we focused on fuzzing the \textit{alphapd} and \textit{mini-httpd} HTTP servers and the application layers of each of the cameras.
@@
 
+\section{Future Work}
+We have many ideas to improve this project in the future.
+One obvious improvement would be to fuzz these devices on multiple protocols, not just the HTTP servers.
+Any one of these other protocols could provide a potential entry point for an attack.
+The testing framework could also be improved by recognizing interesting outputs, and repeating the inputs that caused them with slight mutations.
+This might be a more active approach to identifying interesting vulnerabilities and bugs.
+An HTTP validator could be used to review the responses from the camera servers to verify correct responses and aid in the identification of invalid or buggy responses.
+
+One of the main ideas that we did not have time to implement was to record the video output from each camera during the fuzzing process, and `measure' the quality.
+We would be interested in video lag, frame drops or freezes, or other events that would make the camera unfit for security applications.
+The measure of quality is difficult to define, and was beyond the scope of our current project.
+
 %\begin{figure*}

### 2015-12-05 Draft Paper/Draft_Paper.tex
update
update 2.3.4.5

@@
 \subsection*{Abstract}
-Fuzz testing, or fuzzing, is a simple, automated method to find bugs and vulnerabilities in programs.  
+Fuzz testing, or fuzzing, is a simple, automated method to find bugs and vulnerabilities in programs, where random, potentially invalid inputs are sent.
+Fuzz testing can be much cheaper than other types of testing and often reveals bugs developers and testers cannot foresee.
+After reviewing some current research on fuzzing, we decided an interesting application would be to test `Internet of Things' (IoT) devices like IP cameras.
+We believe that fuzzing a network-connected device can reveal interesting bugs or vulnerabilities, and in the case of security cameras, some of these vulnerabilities may be serious.
 We use fuzzing methods on two different types of Wi-Fi cameras in order to evaluate the efficacy of fuzz testing on these recent types of IoT deployments.
-
-[TODO] Revisit this section after the paper has been more fully fleshed out[TODO]
+We used Pathoc within a Bash shell script framework for crafted malice towards the HTTP servers in these cameras, and ran over 250,000 fuzzing tests.
+We did identify several interesting events and responses from fuzzing tests, but did not identify any critical bugs or serious vulnerabilities in the cameras.
 
@@
 \section{Results}
+We began this project with this question in mind: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} At this point in our research, we have not identified any critical bugs in the cameras or inputs that would completely disable the system.
+We did, however, identify several events or responses that are of interest.
+We were watching the video output of the cameras during some of the fuzz testing, and we did notice some freezing and lagging of the video feed.
+We did not record video or attempt to qualify the video output at this stage of our project.
 
@@
 
-\begin{table}
+[TODO- refine and analyze this cause more]
+We found we could trigger an `HTTP 500 Internal Server Error' with a very long string (70000 byte) in the GET request. The pathoc command looked like 
+\begin{verbatim} pathoc -n 1 -t 5 -e -p -q  $ip 
+`get:@70000,ascii:b@100,ascii:h$auth '  \end{verbatim}
+
+[TODO- add some distributions for the full 250,000 tests, including non-HTTP coded events]
+
+\begin{table}[here]
 \centering

### 2015-12-05 Scripts/Jeff/dataCollect.sh
update scripts

@@ -14,14 +14,35 @@ num2xx=$(grep -c "HTTP/1.[0-1] 2[0-9][1-9]" *[0-9].txt | awk 'BEGIN{FS=":"}{x+=$
 echo "HTTP (non-200) 2XX Returns:$num2xx" >> "DataAggregate_$NOW.txt"
 num300=$(grep -c "HTTP/1.[0-1] 3" *[0-9].txt | awk 'BEGIN{FS=":"}{x+=$2}END{print x}')
 echo "HTTP 3XX Returns:$num300" >> "DataAggregate_$NOW.txt"
-num400=$(grep -c "HTTP/1.[0-1] 4" *[0-9].txt | awk 'BEGIN{FS=":"}{x+=$2}END{print x}')
-echo "HTTP 4XX Returns:$num400" >> "DataAggregate_$NOW.txt"
+num400=$(grep -c "HTTP/1.[0-1] 400" *[0-9].txt | awk 'BEGIN{FS=":"}{x+=$2}END{print x}')
+echo "HTTP 400 Returns:$num400" >> "DataAggregate_$NOW.txt"
+num401=$(grep -c "HTTP/1.[0-1] 401" *[0-9].txt | awk 'BEGIN{FS=":"}{x+=$2}END{print x}')
+echo "HTTP 401 Returns:$num401" >> "DataAggregate_$NOW.txt"
+num403=$(grep -c "HTTP/1.[0-1] 403" *[0-9].txt | awk 'BEGIN{FS=":"}{x+=$2}END{print x}')
+echo "HTTP 403 Returns:$num403" >> "DataAggregate_$NOW.txt"
+num404=$(grep -c "HTTP/1.[0-1] 404" *[0-9].txt | awk 'BEGIN{FS=":"}{x+=$2}END{print x}')
+echo "HTTP 404 Returns:$num404" >> "DataAggregate_$NOW.txt"
+num4xx=$(grep -c "HTTP/1.[0-1] 4[0-9][5-9]" *[0-9].txt | awk 'BEGIN{FS=":"}{x+=$2}END{print x}')
+echo "HTTP 405-499 returns:$num4xx" >> "DataAggregate_$NOW.txt"
+num500=$(grep -c "HTTP/1.[0-1] 500" *[0-9].txt | awk 'BEGIN{FS=":"}{x+=$2}END{print x}')
+echo "HTTP 500 Returns:$num500" >> "DataAggregate_$NOW.txt"
[…]

### 2015-12-05 Scripts/Jeff/fuzz.sh

@@ -45,7 +45,7 @@ do
 	d=$(( ($i*100)/$max ))
 	r=$(( $RANDOM % 100 + 1 )) #Random [1..100]
 	
-pathoc -n 1 -t 5 -e -p -q $ip "$cmd$r$b1$auth" | tee -a "log_$NOW".txt | tee last_cmd.txt | grep 'HTTP/1.1 2*' &> /dev/null
+pathoc -n 1 -t 5 -e -p -q $ip "$cmd$r$b1$auth" | tee -a "log_$NOW".txt | tee last_cmd.txt | grep 'HTTP/1.1 2' &> /dev/null
 
 	if [ $? == 0 ]; then
 		good=$(( $good+1 ))
@@ -80,8 +80,8 @@ do
   r=$(( $RANDOM % 100)) #Random [0-99]
   d=$(( ($i*100)/$max ))
   echo -ne "Percent Done: $d \r"
- modCase=$(( ($i % 7) )) 
-#modCase=3 #force only one case for now
+ #modCase=$(( ($i % 7) )) 
+modCase=1 #force only one case for now
  case $modCase in
 0)
   #valid request with random 50 chars
@@ -126,7 +126,7 @@ esac
 		#echo "$last_out" >> "log_$NOW""_good.txt"
 	else
 		bad=$(( $bad+1 ))
-		grep "HTTP/1.[0-1] 5\|Invalid server response\|Error connecting to" last_cmd.txt
+		grep "HTTP/1.[0-1] 5\|Invalid server response\|Error connecting to\|(null)" last_cmd.txt
 		if [ $? == 0 ]; then
 
 		    last_out=$(<last_cmd.txt)

### 2015-12-10 Draft Paper/Draft_Paper.tex
Paper updates
Updated paper based on Kobus' feedback.

@@
 After reviewing some current research on fuzzing, we decided an interesting application would be to test `Internet of Things' (IoT) devices like IP cameras.
-We believe that fuzzing a network-connected device can reveal interesting bugs or vulnerabilities, and in the case of security cameras, some of these vulnerabilities may be serious.
+With the growing proliferation of these IoT devices, they could become a very attractive target for malicious attacks.
+Attacks on these devices would also greatly compromise security.
 We use fuzzing methods on two different types of Wi-Fi cameras in order to evaluate the efficacy of fuzz testing on these recent types of IoT deployments.
-We used Pathoc within a Bash shell script framework for crafted malice towards the HTTP servers in these cameras, and ran over 250,000 fuzzing tests.
+We used a fuzzing tool called Pathoc within a Bash shell script framework for crafted malice towards the HTTP servers in these cameras, and ran over 250,000 fuzzing tests.
 We did identify several interesting events and responses from fuzzing tests, but did not identify any critical bugs or serious vulnerabilities in the cameras.
@@
 The specific `call for papers' that we target in the presentation of this research is the 9th USENIX Workshop on Offensive Technologies (WOOT '15).
+\url{https://www.usenix.org/conference/woot15/call-for-papers}
 
 \section{Introduction}
-\subsection{Motivation}
 
@@
 
-\subsection{Problem}
-We began this project with some general understanding of fuzzing as a test tool, but without a clear vision of what network services might be interesting or valuable to fuzz.
-After an initial period of exploring current research in fuzzing, we settled on the ultimate goal of our project: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} The project involved several steps: choosing a service to test; deciding how to generate random inputs; determining how to distinguish "good" and "bad" test results; implementing the random tester; and evaluating the effectiveness of the test procedure.
+After an initial period of exploring current research in fuzzing, we settled on this goal: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} Reaching this goal involved several steps: choosing a service to test; deciding how to generate random inputs; determining how to distinguish "good" and "bad" test results; implementing the random tester; and evaluating the effectiveness of the test procedure.
 
-In this project, we started with the goal to design, implement and evaluat an automated tester for a networking service.
-This is meant to evaluate the value of fuzz testing on a network, with the goal of hopefully finding a previously undiscovered bug.
+Initially, we set out to design our own fuzzer, but in researching the subject showed that may tools were already available, which allowed us to focus on trying to find undiscovered bugs and vulnerabilities, instead of the effectiveness of an implementation.
 A very basic and highly proliferated technology deployed on the internet is an HTTP server.
@@
 Therefore, we chose wireless IP cameras as the platform to fuzz test.
-These are some of the most widely available IoT devices for consumers.
+These are some of the most widely available IoT devices for consumers, and could become an attractive entry point for attackers.
 We found that the two devices we purchased ran basic HTTP servers, and we could use tools made for these applications.
-
-One reason we thought it would be interesting as well as important to test these IP cameras is because they are widely used in security systems today.
-It would likely be a bad thing if an outsider could shut down or otherwise impair the function of your security cameras.
-One main goal we had during this experiment was to identify security vulnerabilities in the cameras through fuzzing, to find out if a potential attacker could impair the camera's function.
+If these devices could be accessed by unauthorized third parties, or be made unable to perform their duties, this could be a serious issue.
+We believe that fuzz testing can be an effective way to study if these bugs or vulnerabilities exist.
 
 \section{Related Work}
-In the beginning stages of our project, we explored some recent papers related to fuzzing, to give us a more clear idea of how this test technique is currently implemented and how it is evolving.
-Some of the more interesting papers we came across are detailed below.
+An important first step into researching this process is to obtain a more clear idea of how this test technique was created, hoe it is currently implemented, and how it is evolving.
 
@@
 Therefore, we thought this might be a good starting point for our research.
-We thought this would be interesting because more and more `things' are connecting to the internet today, and all of these `Internet of Things' devices have network protocols that would be interesting to test.
+We thought this would be important because more and more `things' are connecting to the internet today, and all of these `Internet of Things' devices have network protocols that would be interesting to test.
 
-\section{Experiment Setup}
-In this section we describe details about the setup of our experiment, the
-cameras we used, how we gathered information and discovered interesting ways to fuzz test them, and the tools and programs that aided us.
+\section{Experimental Methodology}
+In order to create meaningful experiments, the devices under test had to be purchased and evaluated further.
+Points of attack had to be gathered, evaluated, and implemented in the available tools in order to better attempt to find interesting results.
 
@@
 
-Though the cameras boasted support for many network protocols, most of the functionality was very limited and only supported client protocols.
-Both cameras did have small HTTP servers, though, which we felt were much more interesting to fuzz, as they will more readily accept the inputs that we would give them.
+While the many supported protocols provided many different access points, it was important to identify how the protocol was being implemented.
+The majority of services running on the cameras were client protocols, such as sending SMTP mail or an image transfer via FTP.
+This then gave greater incentive in focusing on the HTTP protocol, as it was the only server.
+The nature of a server is very appealing to an attack, as it is readily available to accept user inputs, and the biggest ``front door" to the cameras.
 
-The first step we took in identifying network protocols that would be interesting and `fuzzable' was to capture some traffic from the cameras in Wireshark~\cite{wireshark}.
+The first step we took in identifying points of access that could be `fuzzable' was to capture some traffic from the cameras in Wireshark~\cite{wireshark}.
 We also looked at the HTML source behind the web pages to discover potential attack points.
@@
 \subsection{Platforms}
-The primary vehicle for running Pathoc in a Bash script was using Oracle's VM VirtualBox 5.0.10 running on two separate Windows 10 laptops.
+The primary vehicle for running Pathoc was a Bash script running on a virtual Linux machine inside Oracle's VM VirtualBox 5.0.10.
+Two different Windows 10 laptops were used to run the VMs.
 One computer ran a 32-bit Ubuntu 12.04 VM with 2.0GiB of dedicated RAM.
@@
 \section{Results}
-We began this project with this question in mind: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} At this point in our research, we have not identified any critical bugs in the cameras or inputs that would completely disable the system.
+We began our research with this question in mind: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} At this point in our research, we have not identified any critical bugs in the cameras or inputs that would completely disable the system.
 We did, however, identify several events or responses that are of interest.

### 2015-12-11 Draft Paper/Draft_Paper.tex
Minor update to paper

@@
 \subsection*{Abstract}
+
+With the growing proliferation of Internet of Things (IoT) devices, they could become a very attractive target for malicious attacks.
+Attacks on these devices, especially ones used for surveillance, would also greatly compromise security.
+A commerically available example of this is a wireless IP camera.
 Fuzz testing, or fuzzing, is a simple, automated method to find bugs and vulnerabilities in programs, where random, potentially invalid inputs are sent.
 Fuzz testing can be much cheaper than other types of testing and often reveals bugs developers and testers cannot foresee.
-After reviewing some current research on fuzzing, we decided an interesting application would be to test `Internet of Things' (IoT) devices like IP cameras.
-With the growing proliferation of these IoT devices, they could become a very attractive target for malicious attacks.
-Attacks on these devices would also greatly compromise security.
-We use fuzzing methods on two different types of Wi-Fi cameras in order to evaluate the efficacy of fuzz testing on these recent types of IoT deployments.
+We use fuzzing methods on two different types of Wi-Fi cameras in order to evaluate the quality of fuzz testing on these recent types of IoT deployments.
 We used a fuzzing tool called Pathoc within a Bash shell script framework for crafted malice towards the HTTP servers in these cameras, and ran over 250,000 fuzzing tests.
@@
 \section{Related Work}
-An important first step into researching this process is to obtain a more clear idea of how this test technique was created, hoe it is currently implemented, and how it is evolving.
 
@@
 	var ptz_type=0;	
-	if(top.client_minor==4) ptz_type=1;
 	var PTZ_STOP=1;
@@
 
-\begin{table}[here]
+\begin{table}[h]
 \centering

### 2015-12-12 Draft Paper/Draft_Paper.tex
Another minor update, needs fixing

@@
 With the growing proliferation of Internet of Things (IoT) devices, they could become a very attractive target for malicious attacks.
-Attacks on these devices, especially ones used for surveillance, would also greatly compromise security.
+Attacks on these devices, especially ones used for surveillance, could also greatly compromise security.
 A commerically available example of this is a wireless IP camera.
@@
 
+A very basic and highly proliferated technology deployed on the internet is an HTTP server.
+But because of this prevalence, popular servers such as Apache have been thoroughly tested and documented.
+However, more and more devices are being connected, with an uptake in the Internet of Things (IoT) mentality.
 Fuzz testing is a method of testing in which random, potentially invalid inputs are sent to a program or service in order to test for vulnerabilities.
@@
 Therefore, many solutions (citations needed) propose a different method where random mutation of good inputs is used so that requests that are close to being correct are used.
+
 Because the world has become more internet-connected than ever, fuzz testing can be an important tool for developers as network-facing interfaces can experience any input, and need to be tested for this randomness.
@@
 Therefore, something as simple as logging into an interface needs to be taken into account in order to get more meaningful tests.
+One question that arises is: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?}
 
-After an initial period of exploring current research in fuzzing, we settled on this goal: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} Reaching this goal involved several steps: choosing a service to test; deciding how to generate random inputs; determining how to distinguish "good" and "bad" test results; implementing the random tester; and evaluating the effectiveness of the test procedure.
-
-Initially, we set out to design our own fuzzer, but in researching the subject showed that may tools were already available, which allowed us to focus on trying to find undiscovered bugs and vulnerabilities, instead of the effectiveness of an implementation.
-A very basic and highly proliferated technology deployed on the internet is an HTTP server.
-But because of this prevalence, popular servers such as Apache have been thoroughly tested and documented.
-However, more and more devices are being connected, with an uptake in the Internet of Things (IoT) mentality.
-Therefore, we chose wireless IP cameras as the platform to fuzz test.
+To address this question, wireless IP cameras were chosen as the platform to fuzz test.
 These are some of the most widely available IoT devices for consumers, and could become an attractive entry point for attackers.
-We found that the two devices we purchased ran basic HTTP servers, and we could use tools made for these applications.
+The two devices we purchased ran basic HTTP servers, and we could use tools made for these applications.
 If these devices could be accessed by unauthorized third parties, or be made unable to perform their duties, this could be a serious issue.
@@
 
-We tried to find research related to fuzzing internet-connected devices, but were unable to.
-Therefore, we thought this might be a good starting point for our research.
-We thought this would be important because more and more `things' are connecting to the internet today, and all of these `Internet of Things' devices have network protocols that would be interesting to test.
+When specifically referring to fuzz testing on IoT devices, we were unable to find much research on this subject. Therefore, we chose this specific field to focus our research.
 
@@
 In order to create meaningful experiments, the devices under test had to be purchased and evaluated further.
-Points of attack had to be gathered, evaluated, and implemented in the available tools in order to better attempt to find interesting results.
+Points of attack were gathered, evaluated, and implemented using the available fuzzing tools in order to better attempt to find interesting results.
 
@@
 \subsubsection{Tools}
-We began by exploring a number of available network fuzzers, including Peach, AutoFuzz, American Fuzzy Lop (AFL), and Pathoc.
-In investigating AFL, we found that it was a tool mainly for file testing, where good files as inputs to tools would be mutated and input back into a program for evaluation.
-We could have used this to create a file with a valid GET request, ran AFL to mutate, and send the file through something like netcat, but this would be more difficult to control in what gets sent to the servers.
-This may be a valuable tool for future work in testing the FTP protocols in the cameras.
-
-AutoFuzz has built in support for MSN, SMTP, and FTP protocols, and relied on capturing actual traffic in order to create a state machine.
-While we did find that both of the cameras used in testing supported both SMTP and FTP, they were only clients, and therefore less likely to accept inputs.
-We attempted to, but were ultimately not able to capture SMTP or FTP traffic from the cameras.
-AutoFuzz did not have support for HTTP, so this tool was abandoned.
-
-Peach was another platform that was looked at extensively.
-The Peach platform relies on ``pits" that define the fields in the standard being tested, as well as the procedure that should be used in testing.
-Their website shows that they have support for protocols such as HTTP, DHCP, IPv4, IPv6, and IoT protocols like CoAP.
-However, these pits are how this company makes money, and we were not willing to purchase them in order to evaluate if they would work for us or not.
-
+Pathoc was used to implement HTTP fuzzing.
 Pathoc turned out to be fairly simple and straightforward to use, as it was just a command line interface tool that generated HTTP requests such as GET and POST.
@@
 
+There are a number of different network fuzzers available, including Peach, AutoFuzz, American Fuzzy Lop (AFL).
+AFL, would be useful as a tool mainly for file testing, where good files as inputs to tools would be mutated and input back into a program for evaluation.
+This may be a valuable tool for future work in testing the FTP protocols in the cameras.
+
+AutoFuzz has built in support for MSN, SMTP, and FTP protocols, and relied on capturing actual traffic in order to create a state machine.
+While both of the cameras used in testing supported both SMTP and FTP, they were only clients, and therefore less likely to accept inputs.
+We attempted to, but were ultimately not able to capture SMTP or FTP traffic from the cameras.
+
+The Peach platform relies on ``pits" that define the fields in the standard being tested, as well as the procedure that should be used in testing.
+Their website shows that they have support for protocols such as HTTP, DHCP, IPv4, IPv6, and IoT protocols like CoAP.
+However, these pits are how this company makes money, and we were not willing to purchase them in order to evaluate if they would work for us or not.
+
 \section{Implementation}
@@
 Pathoc has a built in function to do many requests at one time, but we found that this method had all of the GET requests on a single TCP connection, and therefore made it more difficult to diagnose in programs such as Wireshark.
-Therefore, since Pathoc can easily be implemented using the command line interface, a shell script was used as a wrapper that would invoke Pathoc multiple times, giving a new HTTP request everytime.
+Therefore, since Pathoc can easily be implemented using the Linux command line interface, a shell script was used as a wrapper that would invoke Pathoc multiple times, giving a new HTTP request everytime.
 In this way, we could also control fairly easily the commands for Pathoc to run, instead of having a single command run multiple times.
@@
 \subsection{Platforms}
-The primary vehicle for running Pathoc was a Bash script running on a virtual Linux machine inside Oracle's VM VirtualBox 5.0.10.
-Two different Windows 10 laptops were used to run the VMs.
+Pathoc was run in a Bash script on a virtual Linux machine inside Oracle's VM VirtualBox 5.0.10.
+Two different Windows 10 laptops were used to run the  Linux Virtual Machines (VMs).
 One computer ran a 32-bit Ubuntu 12.04 VM with 2.0GiB of dedicated RAM.
@@
 
-Because these tests can take a significant amount of time, and these computers are also used for other things, a third platform was used to collect fuzzing data.
+Because these tests took a significant amount of time, and these computers were unavailable for long testing runs, a third platform was used to collect fuzzing data.
 A Raspberry Pi 2 model B (RPi) was used so that Pathoc could be run for an extended amount of time (e.g.
@@
 
-Perhaps the first major discovery we made when in the information-gathering stage of the project was that each of the cameras used HTTP Basic or Digest access authentication, which encodes the username:password combinations.
-Wireshark was able to capture the authentication for logging into the cameras in plain text.
-This has important ramifications, because all an attacker would need to do would be to use Wireshark or some other network protocol analyzer to capture traffic on the network the camera is on.
-Once the authentication token is discovered, an attacker could append it to the header of any HTTP message desired, and the camera would accept it as authentic.
-
-We needed a method of weeding out the `good' responses from the `bad' responses. We decided to look at the several categories of HTTP responses: 
+TO weed out the `good' responses from the `bad' responses, the HTTP response codes were examined. There are several categories of HTTP responses: 
 \begin{enumerate}
@@
 
-[EDIT ME]
-As of today [Dec 4,2015] we have run more than 250,700 fuzzing tests.
-We are in the process of aggregating data and trying to understand how best to display it.
-We have not as of yet found any input that would disable the cameras completely, though some inputs do cause slow downs.
+As of Dec 4,2015 we have run more than 250,700 fuzzing tests.
+As of yet, there has not been any input found that would completely disable the cameras.
+However, some inputs do cause slow downs.
 Some of the interesting events like connection timeouts may be much more interesting if we could determine that the reason the connection could not be made was that the server had been disabled or was restarting itself.
@@
 
+A major discovery made, unrelated to fuzzing, occurred in the information-gathering stage of the project.
+Both of the cameras used HTTP Basic or Digest access authentication, which encodes the username:password combinations.
+Wireshark was able to capture the authentication for logging into the cameras in plain text.
+This has important ramifications, because all an attacker would need to do would be to use Wireshark or some other network protocol analyzer to capture traffic on the network the camera is on.
+Once the authentication token is discovered, an attacker could append it to the header of any HTTP message desired, and the camera would accept it as authentic.
+
+\begin{figure}[h b]
+\centering
+\includegraphics[width=1.9\linewidth]{dist}
+\caption{Distribution of 205,000 Response Codes}
+\label{fig:dist}
+\end{figure}
+
 \section{Future Work}
@@
 %\centering
-%\includegraphics[width=0.9\linewidth]{Pyle_Good_CGI}
-%\caption{ 5550 fuzz tests on Pyle camera with valid commands}
-%\label{fig:Pyle_Good_CGI}
-%\end{figure*}
-
-%\begin{figure*}
-%\centering
-%\includegraphics[width=0.9\linewidth]{Pyle_Rand_CGI}
+%\includegraphics[width=1.9\linewidth]{Pyle_Rand_CGI}
 %\caption{5550 fuzz tests on Pyle camera with random commands}

### 2015-12-12 Draft Paper/Draft_Paper.tex
final draft

@@
 \documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{usenix,epsfig,url}
+\usepackage{usenix,epsfig,url,wrapfig}
 \begin{document}
@@
 A very basic and highly proliferated technology deployed on the internet is an HTTP server.
-But because of this prevalence, popular servers such as Apache have been thoroughly tested and documented.
+Because of this prevalence, popular servers such as Apache have been thoroughly tested and documented.
 However, more and more devices are being connected, with an uptake in the Internet of Things (IoT) mentality.
+
 Fuzz testing is a method of testing in which random, potentially invalid inputs are sent to a program or service in order to test for vulnerabilities.
@@
 However, a truly random test input could easily not provide anything useful in a reasonable amount of time.
-Therefore, many solutions (citations needed) propose a different method where random mutation of good inputs is used so that requests that are close to being correct are used.
+Therefore, many solutions propose a different method where random mutation of good inputs is used so that requests that are close to being correct are used.
 
@@
 
-While these papers looked like they had gathered results from their fuzz testing, they did not release their prototype to the public, and therefore we had to find other publicly available tools that would be able to create fuzz tests.
+While these papers showed promising results from their fuzz testing, they did not release their prototypes to the public, and therefore we had to find other publicly available tools that would be able to create fuzz tests.
 A few of the papers read, such as AspFuzz, mentioned the Peach Fuzzing Platform~\cite{peach} as a tool widely used in this type of testing.
@@
 
-When specifically referring to fuzz testing on IoT devices, we were unable to find much research on this subject. Therefore, we chose this specific field to focus our research.
+We were unable to find much research specifically referring to fuzz testing on IoT devices. Therefore, we chose this specific field to focus our research efforts on.
 
 \section{Experimental Methodology}
-In order to create meaningful experiments, the devices under test had to be purchased and evaluated further.
-Points of attack were gathered, evaluated, and implemented using the available fuzzing tools in order to better attempt to find interesting results.
+In order to create meaningful experiments, the cameras under test had to be purchased and evaluated further.
+We gathered information on the cameras, evaluated points of attack, and implemented fuzzing techniques using available tools in order to better attempt to find interesting results.
 
@@
 Though both cameras supported many network protocols, we focused on fuzzing the \textit{alphapd} and \textit{mini-httpd} HTTP servers and the application layers of each of the cameras.
-We thought the HTTP server protocols and application layers would be the most interesting to fuzz.
-Most of the other protocols supported were only client protocols, which we felt would be less interesting to fuzz, yet still valuable.
 We leave testing these other protocols for future work.
@@
 \subsubsection{Tools}
-Pathoc was used to implement HTTP fuzzing.
-Pathoc turned out to be fairly simple and straightforward to use, as it was just a command line interface tool that generated HTTP requests such as GET and POST.
-Because we focused on HTTP, this single protocol application was still very appealing to us.
+We used Pathoc to implement HTTP fuzzing.
+Pathoc turned out to be fairly simple and straightforward to use, as it was just a Linux command line interface tool that generated HTTP requests such as GET and POST.
+Because we focused on HTTP, this single protocol application was very appealing to us.
 This program allowed us to specify the type of HTTP command, and inject whatever we wanted into the header and body fields while still creating a command with valid syntax.
-It also has fuzzing capabilities as it is able to inject random bytes anywhere in the request, as well as generate random strings of a desired length and place them in portions of a request.
+It implements fuzzing by injecting random bytes anywhere in the request, as well as generating random strings of a desired length and placing them in portions of a request.
 Because of its ease of use and the capability to be used in a simple Bash script, we chose Pathoc v0.14 as our fuzzing platform.
 
-There are a number of different network fuzzers available, including Peach, AutoFuzz, American Fuzzy Lop (AFL).
+There are a number of different network fuzzers available, including Peach, AutoFuzz, and American Fuzzy Lop (AFL).
 AFL, would be useful as a tool mainly for file testing, where good files as inputs to tools would be mutated and input back into a program for evaluation.
@@
 AutoFuzz has built in support for MSN, SMTP, and FTP protocols, and relied on capturing actual traffic in order to create a state machine.
-While both of the cameras used in testing supported both SMTP and FTP, they were only clients, and therefore less likely to accept inputs.
+While the cameras used in testing supported both SMTP and FTP, they were only clients, and therefore less likely to accept inputs.
 We attempted to, but were ultimately not able to capture SMTP or FTP traffic from the cameras.
@@
 For example \textit{\$cmd} might represent an HTTP GET or POST, \textit{\$b1} represents the contents of the HTTP body, and \textit{\$auth} represents the header with authentication credentials.
-The output is checked, and server responses with \textbf{HTTP/1.1 200} are marked `good' and all others are marked `bad'.
+The output is checked, and server responses with HTTP/1.1 200 are marked `good' and all others are marked `bad'.
 \begin{verbatim}
@@
 
-It is important to note that if the server doesn't respond with \textbf{HTTP/1.1 200}, it does not necessarily mean that it is bad.
+It is important to note that if the server doesn't respond with HTTP/1.1 200, it does not necessarily mean that it is bad.
 This is just the metric we used to try and identify possible interesting responses.
@@
 
-We also wrote a separate script to scour the log files and aggregate the total number of responses in various categories.
-We used some of this data for the Pyle camera to generate tables~\ref{tab:Pyle_Good_CGI} and ~\ref{tab:Pyle_Rand_CGI}.
+We also wrote a separate script to scour the log files and aggregate the total number of responses in various categories. We used some of this data for the Pyle camera to generate tables 1 through 3.
 
 \subsection{Platforms}
-Pathoc was run in a Bash script on a virtual Linux machine inside Oracle's VM VirtualBox 5.0.10.
-Two different Windows 10 laptops were used to run the  Linux Virtual Machines (VMs).
+Two different Windows 10 laptops were used to run Linux Virtual Machines (VMs) using Oracle's VM VirtualBox 5.0.10.
 One computer ran a 32-bit Ubuntu 12.04 VM with 2.0GiB of dedicated RAM.
@@
 We were watching the video output of the cameras during some of the fuzz testing, and we did notice some freezing and lagging of the video feed.
-We did not record video or attempt to qualify the video output at this stage of our project.
+We did not record video or attempt to qualify the video output at this stage.
 
-TO weed out the `good' responses from the `bad' responses, the HTTP response codes were examined. There are several categories of HTTP responses: 
+It was necessary to weed out the `good' responses from the `bad' responses, so the HTTP response codes were examined. There are several categories of HTTP responses: 
 \begin{enumerate}
@@
 \end{enumerate}
-We decided to categorize all but HTTP 2xx responses as `bad'. We also discovered other interesting events:
+We decided to categorize all but HTTP 2xx responses as `bad'. We were most interested in the HTTP 5xx responses, as these indicated server errors. We also discovered other interesting events:
 \begin{enumerate}
@@
 
-As of Dec 4,2015 we have run more than 250,700 fuzzing tests.
+Throughout the course of ten days, we ran more than 250,700 fuzzing tests.
+Figure 1 shows a distribution of responses for a significant portion of the tests run.
 As of yet, there has not been any input found that would completely disable the cameras.
 However, some inputs do cause slow downs.
-Some of the interesting events like connection timeouts may be much more interesting if we could determine that the reason the connection could not be made was that the server had been disabled or was restarting itself.
+Some events like connection timeouts may be much more interesting if we could determine the specific reason the connection could not be made.
 There is future work in further analyzing the data that we have collected.
@@
 
-An interesting result was also the difference in the time taken to run the same command on a Ubuntu VM comapred to the Raspberry Pi.
+An interesting result was also the difference in the time taken to run the same command on a Ubuntu VM compared to the Raspberry Pi.
 We noticed that although the small computer is very powerful, it had a significant time overhead in our setup.
 The results of a test consisting of 5000 valid CGI commands to the Pyle camera is shown in table~\ref{tab:VMvsPi}.
-As we can see, they both generated a similar amount of HTTP responses in the 400 and 500 range, but the Rpi took almost 450\% longer to do it.
+As we can see, they both generated a similar number of HTTP responses in the 4xx and 5xx range, but the Rpi took almost 450\% longer to do it.
 We suspect it may have to do with the smaller computer having slower I/O speeds for both the USB flash drive and the network interface.
@@
 
-[TODO- refine and analyze this cause more]
 We found we could trigger an `HTTP 500 Internal Server Error' with a very long string (70000 byte) in the GET request. The pathoc command looked like 
@@
 `get:@70000,ascii:b@100,ascii:h$auth '  \end{verbatim}
-
-[TODO- add some distributions for the full 250,000 tests, including non-HTTP coded events]
 
@@
 
-A major discovery made, unrelated to fuzzing, occurred in the information-gathering stage of the project.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=2\linewidth]{dist}
+	\caption{Distribution of 204,691 Response Codes}
+	\label{fig:dist}
+\end{figure}
+
+A major discovery, unrelated to fuzzing, occurred in the information-gathering stage of our research.
 Both of the cameras used HTTP Basic or Digest access authentication, which encodes the username:password combinations.
@@
 Once the authentication token is discovered, an attacker could append it to the header of any HTTP message desired, and the camera would accept it as authentic.
-
-\begin{figure}[h b]
-\centering
-\includegraphics[width=1.9\linewidth]{dist}
-\caption{Distribution of 205,000 Response Codes}
-\label{fig:dist}
-\end{figure}
+It would be possible to completely disable the camera by assigning it to be on a different unreachable network.
 
 \section{Future Work}
-We have many ideas to improve this project in the future.
+We have many ideas to continue this research in the future.
 One obvious improvement would be to fuzz these devices on multiple protocols, not just the HTTP servers.
@@
 An HTTP validator could be used to review the responses from the camera servers to verify correct responses and aid in the identification of invalid or buggy responses.
-
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
+\newline
 One of the main ideas that we did not have time to implement was to record the video output from each camera during the fuzzing process, and `measure' the quality.
 We would be interested in video lag, frame drops or freezes, or other events that would make the camera unfit for security applications.
-The measure of quality is difficult to define, and was beyond the scope of our current project.
-
-%\begin{figure*}
-%\centering
-%\includegraphics[width=1.9\linewidth]{Pyle_Rand_CGI}
-%\caption{5550 fuzz tests on Pyle camera with random commands}
-%\label{fig:Pyle_Rand_CGI}
-%\end{figure*}
+The measure of quality is difficult to define, and was beyond the scope of this research.
 
 \subsection*{Acknowledgments}
-We would like to thank our shepherd, Dr. Eric Eide in providing invaluable insight and assistance with two poor ECE students completing a CS project.
+We would like to thank our mentor, Dr. Eric Eide in providing invaluable insight and assistance during the course of this research.
 
